---
title: '6060 Practice: RMarkdown'
author: "Brooke Charbonneau"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)

#Load data 
analytic_data_female        <- read_csv("analytic_data_female.csv")

```

# Relations among variables for women

Below are the correlations among the variables for women.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
psych::pairs.panels(analytic_data_female)      
```

\pagebreak

# Distributions

## Distribution of negative affect scores

Below we can see the distribution of negative affect scores is skewed.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.hist.neg <- ggplot(analytic_data_female,aes(neg_affect))
my.hist.neg <- my.hist.neg + geom_histogram(aes(y=..count..), binwidth = .1, fill="gray40",color="gray40")
my.hist.neg <- my.hist.neg + labs(title="",x="Negative Affect",y="Frequency")
my.hist.neg <- my.hist.neg + theme_classic()
my.hist.neg <- my.hist.neg + theme(axis.line.x = element_line(colour = 'black',size=0.5, linetype='solid'),
                                     axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
my.hist.neg <- my.hist.neg + scale_x_continuous(breaks = seq(0,3,by=1))
my.hist.neg <- my.hist.neg + scale_y_continuous( expand = c(0,0))
print(my.hist.neg)
```

\pagebreak

## Neuroticism Distribution

Below we can see the distribution of neuroticism scores is relatively normal.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.hist.neur <- ggplot(analytic_data_female,aes(Neuroticism))
my.hist.neur <- my.hist.neur + geom_histogram(aes(y=..count..), binwidth = .75, fill="gray40",color="gray40")
my.hist.neur <- my.hist.neur + labs(title="",x="Neuroticism",y="Frequency")
my.hist.neur <- my.hist.neur + coord_cartesian(xlim=c(0,25), ylim = c(0,1200))
my.hist.neur <- my.hist.neur + theme_classic()
my.hist.neur <- my.hist.neur + theme(axis.line.x = element_line(colour = 'black',size=0.5, linetype='solid'),
                                     axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
my.hist.neur <- my.hist.neur + scale_y_continuous(breaks = seq(0,1200,by=300), expand = c(0,0))
print(my.hist.neur)
```

\pagebreak

# Relations among variables

## Scatter plot for Negative Affect and Neuroticism

Below you can see the correlation between negative affect and neuroticism with a regression line.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.scatter <- qplot(x=neg_affect,y=Neuroticism,data=analytic_data_female)
my.scatter <- my.scatter + geom_smooth(method = "lm", se = FALSE, color='black')
my.scatter <- my.scatter + labs(title="",x="Negative Affect",y="Neuroticism")
my.scatter <- my.scatter + theme_classic()
my.scatter <- my.scatter + theme(axis.line.x = element_line(colour = 'black',size=0.5, linetype='solid'),
                                     axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

print(my.scatter)
```

